---
title: "Hot Spots- data clean up"
output: html_notebook
---

The purpose of this script is to clean up and modify the data PSRE parasite 
infection data from the Bay Area of Califronia from 2009 - 2015

The purpose of this data is to utilize a guassian process model to understand
spatial and temporal patterns of hot spots of parasite load. 


Setting the working directory and entering the data below

```{r}
setwd("/Users/travismcdevitt-galles/Desktop/Current_Projects/Hot-Spots")

raw.df <- read.csv("./Raw_Data/raw_host_spots.csv")

names(raw.df)

```

Currently this inital data format includes the follow:

Meta data
    Site year - combination of site code and year sampled 
    assessment code - Combination of site code and year month and day sampled
    Year - year sampled
    Site code - site code 
    Site name - name of site
    years_sampled_2009 - number of times sampled since 2009 : range from 1-6
    PropertyName_1 - The owner of the property the site is found in
    MetaComm_1 - the metacommunity where the site is locater n =  9
    County - the specific county the site is found in
    FULLSAMPLE : 1 or 0 , whether or not it was a full sample 
                a full sample is doing dip nets and collecting both frogs and
                snails
    Latitude_1 : the latitude of the site
    Longitude_1 : the longitude of the site
    PONDAREA : the area of the sites
    PERIMETER : the perimeter of the site ( this was take more consistent than
                area)
    Sweeps1 : Number of dipnet sweeps done at visit: range 0 - 18
    PSRE_SW_1 : number of PSRE larvae per sweep , metric of host density
    HELI_.SW_1 : number of the intermediate host detected per sweep
    psrediss3 : number of PSRE dissected to quantify parasite load:
                range 0 - 60 ( HOLY SHIT 60 IS A LOT!!!!)
    PSREECHINO_3 : mean level Echino infection per PSRE dissected
    PSRERIB_3 : mean level of RIB infection per PSRE dissected

    
 Next step is to identify any problems with the data set
 
```{r, echo=F}

unique(raw.df$SiteCode_1) # sites look good

unique(raw.df$AssmtYear_1) # years look good

unique(raw.df$years_sampled_2009) # looks good

unique(raw.df$PropertyName_1)  # one issue the nature conservancy

for( i in 1:nrow(raw.df)){
    if( raw.df$PropertyName_1[i] == "The Nature conservancy Kammerer Ranch" ){
    raw.df$PropertyName_1[i] <- "The Nature Conservancy Kammerer Ranch"
    }
}

unique(raw.df$MetaComm_1) # looks good

unique( raw.df$County)

```


Issues with either typos or discrepencies between groups


Next step to add an addition variable, total rib and total echino observed

```{r}



```


