---
title: "Hot Spots : Exploring Guassian Processes in disease hot spots"
output: html_notebook
---

Reading in the data and loading the required packages

```{r}

setwd("/Users/travismcdevitt-galles/Desktop/Current_Projects/Hot-Spots")

library(tidyverse)
library(rethinking)

raw.df <- read.csv("./Data/Clean_up_Data/full_dissect.csv")

raw.df <- raw.df[,-1]


```

The initial  attempt would be to look at spatial correlation structure at the
site across all years, then potentially break it down by year to see if the 
spatial signature changes

*** Still need to think how to plot these values ???



Constructing the distance matrix between all sites

```{r}

# For the first model constution I will focus on all sites without subsetting 
# based on number of total visits later models i will focus on sites that meet
#  a particular criteria such as number of sampleing events > 3 

# Below function pulls out all distinct sitename and its corresponding lat and 
# long

distinct_df <- raw.df %>%
                group_by(SiteName, Latitude_1, Longitude_1) %>%
                distinct(SiteName)

# Distance matrix based on euclidian distance from lat and long in meters
dist_mat <- geosphere::distm(distinct_df[,3:2]) 

# adding row and column names

rownames(dist_mat) <- distinct_df$SiteName
colnames(dist_mat) <- distinct_df$SiteName


```

First attempt at building an all year spatial GP model

lets do this shit

```{r}

# making all rib count intergers

raw.df$Total_RIB <- as.integer(round( raw.df$Total.RIB ,0))

GP_Rib_m1 <- map2stan(
    alist(
        Total_RIB ~ dgampois( lambda, scale),
        log( lambda ) <-  s[year] + 1*log(psrediss3),
        #a ~ dnorm(0,10), # global intercept
        s[year] ~ dnorm(0,10) , # adjustment for year
        b <- 1, # fixed value for our offset
        scale ~ dcauchy(0,1) # overdisersion parameter for our gamma poisson 
       # gp[SiteName] ~ GPL2( dist_mat, etasq, rhosq, theta), # GP process
        #etasq ~ dcauchy(0,1), # eta prior for max covaraince
        #rhos ~ dcauchy(0,1), # rho prior for decay rate
        #theta ~ dcauchy(0,1) # within site level covariance prior
    ) ,
    data = list(
        Total_RIB = raw.df$Total_RIB,
        year = as.factor(raw.df$AssmtYear_1),
        SiteName = raw.df$SiteName,
        psrediss3 = raw.df$psrediss3,
        dist_mat = as.matrix(dist_mat)
    ) ,
    warmup = 2000,
    iter = 1e4,
    chains = 4
)


precis(GP_Rib_m1, depth= 2)



year.sum <- raw.df %>% group_by(AssmtYear_1) %>%
    summarise( m.rib = mean(PSRERIB_3))

year.sum
```


So building one giant models seems tricky, so instead lets simply break
down the 

We will start with the year 2009

```{r}



```