---
title: "Hot Spots : Exploring Guassian Processes in disease hot spots"
output: html_notebook
---

Reading in the data and loading the required packages

```{r}

setwd("/Users/travismcdevitt-galles/Desktop/Current_Projects/Hot-Spots")

library(tidyverse)
library(rethinking)

raw.df <- read.csv("./Data/Clean_up_Data/full_dissect.csv")

raw.df <- raw.df[,-1]


```

The initial  attempt would be to look at spatial correlation structure at the
site across all years, then potentially break it down by year to see if the 
spatial signature changes

*** Still need to think how to plot these values ???



Constructing the distance matrix between all sites

```{r}

# For the first model constution I will focus on all sites without subsetting 
# based on number of total visits later models i will focus on sites that meet
#  a particular criteria such as number of sampleing events > 3 

# Below function pulls out all distinct sitename and its corresponding lat and 
# long

distinct_df <- raw.df %>%
                group_by(SiteName, Latitude_1, Longitude_1) %>%
                distinct(SiteName)

# Distance matrix based on euclidian distance from lat and long in meters
dist_mat <- geosphere::distm(distinct_df[,3:2]) 

# adding row and column names

rownames(dist_mat) <- distinct_df$SiteName
colnames(dist_mat) <- distinct_df$SiteName


```

First attempt at building an all year spatial GP model

lets do this shit

```{r}

# making all rib count intergers

all_year_df <- raw.df


GP_Rib_m1 <- map2stan(
    alist(
        Total_RIB ~ dgampois( lambda, scale),
        log( lambda ) <-  s[year] + 1*log(psrediss3),
        #a ~ dnorm(0,10), # global intercept
        s[year] ~ dnorm(0,10) , # adjustment for year
        b <- 1, # fixed value for our offset
        scale ~ dcauchy(0,1) # overdisersion parameter for our gamma poisson 
        gp[SiteName] ~ GPL2( dist_mat, etasq, rhosq, theta), # GP process
        etasq ~ dcauchy(0,1), # eta prior for max covaraince
        rhosq ~ dcauchy(0,1), # rho prior for decay rate
        theta ~ dcauchy(0,1) # within site level covariance prior
    ) ,
    data = list(
        Total_RIB = raw.df$Total_RIB,
        year = as.factor(raw.df$AssmtYear_1),
        SiteName = raw.df$SiteName,
        psrediss3 = raw.df$psrediss3,
        dist_mat = as.matrix(dist_mat)
    ) ,
    warmup = 2000,
    iter = 1e4,
    chains = 4
)


precis(GP_Rib_m1, depth= 2)



year.sum <- raw.df %>% group_by(AssmtYear_1) %>%
    summarise( m.rib = mean(PSRERIB_3))

year.sum
```


So building one giant models seems tricky, so instead lets simply break
down the 

We will start with the year 2009

```{r}
yr09_df <- filter( raw.df, AssmtYear_1 == 2009 )

yr09_df$site_index <- 1:nrow(yr09_df)
distinct_df <- yr09_df %>%
                group_by(SiteName, Latitude_1, Longitude_1) %>%
                distinct(SiteName)

# Distance matrix based on euclidian distance from lat and long in meters
dist_mat <- geosphere::distm(distinct_df[,3:2]) 

# adding row and column names

rownames(dist_mat) <- distinct_df$SiteName
colnames(dist_mat) <- distinct_df$SiteName

dist_mat_km <- dist_mat/1000


GP_Rib_09 <- map2stan(
    alist(
        Total_RIB ~ dgampois( lambda, scale),
        log( lambda ) <- gp[SiteName] + 1*log(psrediss3),
        #tercept
        b <- 1, # fixed value for our offset
        scale ~ dcauchy(0,1), # overdisersion parameter for our gamma poisson 
        gp[SiteName] ~ GPL2( dist_mat, etasq, rhosq, 0.1 ), # GP process
        etasq ~ dcauchy(0,1), # eta prior for max covaraince
        rhosq ~ dcauchy(0,1) # rho prior for decay rate
    ) ,
    data = list(
        Total_RIB = yr09_df$Total_RIB,
        SiteName = yr09_df$site_index,
        psrediss3 = yr09_df$psrediss3,
        dist_mat = as.matrix(dist_mat_km)
    ) ,
    warmup = 2000,
    iter = 1e4,
    chains = 4
)

precis(GP_Rib_09,depth=2)

# extracting the posteriors for the 09 model

post_09 <- extract.samples(GP_Rib_09)

# plotting the decay rate


curve( median(post_09$etasq)*exp(-median(post_09$rhosq) * x^2), from=0,
       to=5, ylab = "Covariance", xlab="Distance in km", lwd=3, main="2009")

for( i in 1:150){
    curve(post_09$etasq[i]*exp(- post_09$rhosq[i] * x^2) , add=T, 
    col = col.alpha("black", .2) )
}


```


Working on 2010

```{r}
yr10_df <- filter( raw.df, AssmtYear_1 == 2010 )

yr10_df$site_index <- 1:nrow(yr10_df)
distinct_df <- yr10_df %>%
                group_by(SiteName, Latitude_1, Longitude_1) %>%
                distinct(SiteName)

# Distance matrix based on euclidian distance from lat and long in meters
dist_mat <- geosphere::distm(distinct_df[,3:2]) 

# adding row and column names

rownames(dist_mat) <- distinct_df$SiteName
colnames(dist_mat) <- distinct_df$SiteName

dist_mat_km <- dist_mat/1000


GP_Rib_10 <- map2stan(
    alist(
        Total_RIB ~ dgampois( lambda, scale),
        log( lambda ) <- gp[SiteName] + 1*log(psrediss3),
        #tercept
        b <- 1, # fixed value for our offset
        scale ~ dcauchy(0,1), # overdisersion parameter for our gamma poisson 
        gp[SiteName] ~ GPL2( dist_mat, etasq, rhosq, 0.1 ), # GP process
        etasq ~ dcauchy(0,1), # eta prior for max covaraince
        rhosq ~ dcauchy(0,1) # rho prior for decay rate
    ) ,
    data = list(
        Total_RIB = yr10_df$Total_RIB,
        SiteName = yr10_df$site_index,
        psrediss3 = yr10_df$psrediss3,
        dist_mat = as.matrix(dist_mat_km)
    ) ,
    warmup = 2000,
    iter = 1e4,
    chains = 4
)

precis(GP_Rib_10,depth=2)

# extracting the posteriors for the 09 model

post_10 <- extract.samples(GP_Rib_10)

# plotting the decay rate


curve( median(post_10$etasq)*exp(-median(post_10$rhosq) * x^2), from=0,
       to=5, ylab = "Covariance", xlab="Distance in km", lwd=3, main="2010")

for( i in 1:150){
    curve(post_10$etasq[i]*exp(- post_10$rhosq[i] * x^2) , add=T, 
    col = col.alpha("black", .2) )
}


```